What's in a Domain?: Feature Engineering for URLs

### 2022-09-19 paper/paper.tex
References

Litrature review

Write a literature review \cite{Vazhayil2018}
\cite{Canali2011}
\cite{Ayes2019}
\cite{Mamun2016}
\cite{Li2020}
\cite{Basnet2012}
\cite{Basnet2014}
\cite{Tupsamudre2019}
\cite{Le2018}
\cite{Baykan2009}
\cite{Kan2005}
\cite{Hernandez2012}
\cite{Chung2022}
\cite{Qiu2020}
\cite{Vaishnavi2021}
\cite{Xu2021}
\cite{Rhea2022}

>>>>

The Uniform Resource Locator (URL) is now a ubiquitous element of modern life. 
We use them to advertise and locate businesses, to retrieve news and media and 
to interact with other people across a broad of social applications. It should
be no surprise that processing URLs is key component of many tasks that involve
analysing internet data. In many applications the URL is the central piece of 
information available because the demands of the task require immediate analysis.
Prominent examples include security analysis of potenital phishing attacks\cite{Basnet2014}, 
detection of potential spam emails \cite{}, and applications to online advertsing
including anticipation of conversions \cite{Qiu2020} or contextual analysis of
the content of webpages\cite{Kan2005,Baykan2009}.

The URL is made up of multiple elements, but at its core is the domain. The domain
contains internal information about both its intended purpose, legitimacy and likely
origin. It is also a source of additional information through requests to Domain Name
Servers (DNS) to understand both its history and place within the network topology.

Common feature engineering strategies exploit these potential sources of information
in ways that are appropriate for a given task. However, while there are wide variety
of approaches that inconsistently applied, there has not yet been a study that evaluates
the overall effectiveness of different strategies across a range of applications.

In this work we describe an ontology of URL fetaures that relates to underlying origin
and purpose. We then present an open source package for generating features within these
ontologocal classes and apply them to a variety of tasks. We present our results as a
cross-task evaluation of URL features.

Multiple data science and machine learning applications on internet data 
Write a literature review \cite{Vazhayil2018}
\cite{Canali2011}
\cite{Ayes2019}
\cite{Mamun2016}
\cite{Li2020}
\cite{Basnet2012}
\cite{Basnet2014}
\cite{Tupsamudre2019}
\cite{Le2018}
\cite{Baykan2009}
\cite{Kan2005}
\cite{Hernandez2012}
\cite{Chung2022}
\cite{Qiu2020}
\cite{Vaishnavi2021}
\cite{Xu2021}
\cite{Rhea2022}

Common approaches to feature engineering on URLs include string matching and regular expressions to
identify key sequences \cite{}, generation of task specific embedding vectors\cite{Qiu2020} and the
usage of domain name servers or registrars for ancillary information \cite{}
